\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{fontawesome}
\usepackage{geometry}
\usepackage{ragged2e}
\hyphenpenalty=5000
\begin{document}

\part{\textbf{Abhishek} Kumar}



\personal
    [abhishekkumar@unomaha.edu]
    {Abhishek Kumar}
    {(402)-321-2639}
    {akamazing}


\section{Education}

\begin{yearlist}

\item{2016 -- 2018}
     {University of Nebraska, Omaha}
     {M.S., Computer Science}

\item{2012 -- 2016}
     {IIT, Kharagpur, India}
     {B.Tech., Computer Science and Engineering}


\end{yearlist}

\section{Professional Experience}

\begin{experiencelist}

\item{Aug '17 -- Present}
     {UNO{}}
     {Graduate Assistant}
     {Working on an efficient algorithm to extract information content from modulated radio waves.}

\item{Aug '16 -- Jan '17}
     {Infofree.com{}, Omaha}
     {Research Assistant}
     {Worked on automating the build processes of database. Reduced the build process time by using external sort on large files in chunks. Prepared and implemented documentation for Infofree API portal.}

\item{May '15 -- July ’15}
     {Infofree.com{}, Omaha}
     {\mbox{Software Engineering Intern}}
     {Defined standard fields for the customer files from the company's database, and wrote a web service using JAVA that maps a given customer's file to the previously defined standard format. Designed and developed a web service that removes duplicate records from two files based on different match rules using Hadoop clusters.}

\end{experiencelist}


\section{Skills}

\begin{factlist}

\item{Programming}
     {Java, C, C++, Python, HTML, CSS, JavaScript, MySQL.}

\item{Frameworks}
     {Selenium, TensorFlow, Ember.js, Django.}

\item{DevOps/Infra}
     {Firebase, Git, Heroku, Docker, AWS.}

\end{factlist}

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

\section{Academic Projects}

\begin{projectlist}

\item{Metamorphic testing of Machine learning algorithms}
     {python, TensorFlow}

Testing the popular TensorFlow machine learning implementation using metamorphic relations.

\item{Blockchain \& cryptocurrency}
     {JAVA}

Exploring and implementing the blockchain structure and mining strategies.

\item{Poiesis - A carpooling app}
     {Ember.js, Firebase}

A carpooling app for the guardians of middle school students, that will help them take the kids to school safe and on time.

\item{Coloring $\beta$-frugal graphs}
     {Python}

Implemented a randomized algorithm for the $\beta$-frugal coloring of graphs and hypergraphs as well as planar and interval graphs, with the help of asymmetric Lov\'{a}sz Local Lemma.


\item{Transport Company Management System}
     {HTML, PHP, MySQL}

Developed an application to support the needs of retailers, manufacturers, distributors, and logistics service providers. The software enables companies to manage customers, bookings, modes of transport, freight payment and billing.

\item{Runtime Summarization of Tweets During Disaster}
     {Python}

Implemented a tweet summarization technique to generate online summaries from ranked clusters of tweets, following an abstractive extractive approach.

\item{WSDM CUP}
     {Python, weka}

Developed a machine learning model to  provide the best static rank values for publication entities in Microsoft Academic Graph.

\item{Hotel Automation Software}
     {JAVA Swing, MySQL}

An application that automates all the operations of a hotel. The software organizes everything from room rates, room availability, booking, and billing to catering services.



\end{projectlist}

\end{document}
